\begin{thebibliography}{999}

\bibitem[Mohamed(2021)]{Mohamed2021} %01
Mohamed,N.; Mustafa,M.B.; Jomhari,N. A Review of the Hand Gesture Recognition System: Current Progress and Future Directions. {\em IEEE Access} {\bf 2021}, {\em 9}, 157422--157436.

\bibitem[Rautaray(2015)]{Rautaray2015} %02
Rautaray, S.S.; Agrawal, A.  Vision based hand gesture recognition for human computer interaction: a survey. {\em Artificial Intelligence Review} {\bf 2015}

\bibitem[Liu(2018)]{Liu2018} %03
Liu, H.; Wang, L.  Gesture recognition for human-robot collaboration: A review. {\em International Journal of Industrial Ergonomics} {\bf 2018}, {68}

\bibitem[Ajoudani(2018)]{Ajoudani2018} %04
Ajoudani, A.;  Zanchettin, A. M.; Ivaldi, S.; Albu-Schäffer, A.; Kosuge, K.; Khatib, O. Progress and prospects of the human–robot collaboration. {\em AR} {\bf 2018}, {\em 42}, 957--975.

\bibitem[El Zaatari(2019)]{ElZaatari2019} %5
El Zaatari, S.; Marei, M.; Li, W.; Usman, Z. Cobot programming for collaborative industrial tasks: An overview. {\em RAS} {\bf 2019}, {\em 116}, 162--180.

\bibitem[Gualtieri(2021)]{Gualtieri2021} %06
Gualtieri, L.; Rauch, E.; Vidoni, R. Emerging research fields in safety and ergonomics in industrial collaborative robotics: A systematic literature review. {\em RCIM} {\bf 2021}, {\em 67}

\bibitem[Castro(2021)]{Castro2021} %07
Castro, A.; Silva, F.; Santos, V. Trends of human-robot collaboration in industry contexts: Handover, learning, and metrics. {\em Sensors} {\bf 2021}, {\em 21}

\bibitem[Bonci(2021)]{Bonci2021} %08
Bonci,A.; Cheng,P.D.C.; Indri,M.; Nabissi,G.; Sibona,F. Human-robot perception in industrial environments: A survey. {\em Sensors} {\bf 2021}, {\em 21}, 1--29.

\bibitem[Hjorth(2021)]{Hjorth2022} %08
Hjorth, S; Chrysostomou, D. Human–robot collaboration in industrial environments: A literature review on non-destructive disassembly. {\em RCIM} {\bf 2022}, {\em 73}

\bibitem[Neto(2019)]{Neto2019} %09
Neto, P.; Simão,M.; Mendes, N.; Safeea, M. Gesture-based human-robot interaction for human assistance in manufacturing. {\em IJAMT} {\bf 2019}, {\em 101}, 119--135.

\bibitem[AlFarid(2021)]{AlFarid2022} %10
Al Farid,F.; Hashim,N.; Abdullah,J.; Bhuiyan,M.R.; Shahida Mohd Isa, W.N.; Uddin,J.; Haque,M.A.; Husen,M.N. A Structured and Methodological Review on Vision-Based Hand Gesture Recognition System. {\em Journal of Imaging} {\bf 2022}, {\em 8}

\bibitem[Oudah(2020)]{Oudah2020} %11
Oudah,M.; Al-Naji,A.; Chahl,J. Hand Gesture Recognition Based on Computer Vision: A Review of Techniques. {\em Journal of Imaging} {\bf 2020}, {\em 6}

\bibitem[Sarma(2021)]{Sarma2021} %12
Sarma,D.; Bhuyan,M.K. Methods, Databases and Recent Advancement of Vision-Based Hand Gesture Recognition for HCI Systems: A Review. {\em SN Computer Science} {\bf 2021}, {\em 2}

\bibitem[Dignan(2022)]{Dignan2022} %13
Dignan,C.;Perez,E.;Ahmad,I.;Huber,M.;Clark,A. An AI-based Approach for Improved Sign Language Recognition using Multiple Videos. {\em Multimed. Tools Appl.} {\bf 2022}, {\em 81(24)}, 34525--34546.

\bibitem[Subramanian(2022)]{Subramanian2022} %14
Subramanian,B.;Olimov,B.;Naik,S.M.;Kim,S.;Park,K.H.;Kim,J. An integrated mediapipe-optimized GRU model for Indian sign language recognition. {\em Sci. Rep.} {\bf 2022}, {\em 12(1)}

\bibitem[Qi(2021)]{Qi2021} %15
Qi,J.; Xu,K.; Ding,X. Approach to hand posture recognition based on hand shape features for human–robot. {\em Complex and Intelligent Systems} {\bf 2022}, {8}, 2825--2842.

\bibitem[Sarma(2022)]{Sarma2022} %16
Sarma,D.; Bhuyan,M.K. Hand Detection by Two-Level Segmentation with Double-Tracking and Gesture Recognition Using Deep-Features. {\em Sensing and Imaging} {\bf 2022}, {23}

\bibitem[Nuzzi(2019)]{Nuzzi2019} %17
Nuzzi,C.; Pasinetti,S.; Lancini,M.; Docchio,F.,Sansoni, G. Deep learning-based hand gesture recognition for collaborative robots {\em IEEE Instrumentation \& Measurement Magazine} {\bf 2019}

\bibitem[Mujahid(2021)]{Mujahid2021} %18
Mujahid,A.; Awan,M.J.; Yasin,A.; Mohammed,M.A.; Damaševičius, R.; Maskeliūnas,R.; Abdulkareem,K.H. Real-time hand gesture recognition based on deep learning YOLOv3 model. {\em Applied Sciences (Switzerland)} {\bf 2021}, {11}

\bibitem[Deng(2009)]{Deng2009} %19
Deng,J.;Dong,W.;Socher,R.;Li,L.;Kai,L.;Li,F. ImageNet: A large-scale hierarchical image database. {\em 2009 IEEE CVPR} {\bf 2009}, 248–-255

\bibitem[Du(2017)]{Du2017} %20
Du, Y.; Jin, W.; Wei, W.; Hu, Y.; Geng, W.  Surface EMG-based intersession gesture recognition enhanced by deep domain adaptation. {\em Sensors} {\bf 2017}, {17(3)}

\bibitem[Zou(2021)]{Zou2021} %21
Zou, Y.; Cheng, L.  A Transfer Learning Model for Gesture Recognition Based on the Deep Features Extracted by CNN. {\em IEEE Transactions on Artificial Intelligence} {\bf 2021}, {2(5)}

\bibitem[Wu(2021)]{Wu2021} %22
Wu, B.X.; Guang, C.; Zhong, J.P.  Research on Transfer Learning of Vision-based Gesture Recognition. {\em International Journal of Automation and Computing} {\bf 2021}, {18(3)}

\bibitem[Zhang(2022)]{Zhang2022} %23
Zhang, Y.; Wu, L.; He, W.; Zhang, Z.; Yang, C.; Wang, Y., Wang, Y., Tain, K.  An Event-Driven Spatiotemporal Domain Adaptation Method for DVS Gesture Recognition. {\em IEEE Transactions on Circuits and Systems II: Express Briefs} {\bf 2022}, {69(3)}

\bibitem[Wang(2018)]{Wang2018} %24
Wang, M.; Deng, W.  Deep visual domain adaptation: A survey. {\em Neurocomputing} {\bf 2018}, {312}

\bibitem[Yang(2020)]{Yang2020} %25
Yang, Q.; Zhang, Y.; Dai, W.; Jialin, S.  Adversarial Transfer Learning. {\em Transfer Learning} {\bf 2020}

\bibitem[Yasen(2019)]{Yasen2019} %26
Yasen, M.; Jusoh,S. A systematic review on hand gesture recognition techniques, challenges and applications. {\em PeerJ Computer Science} {\bf 2019}

\bibitem[Ryumin(2023)]{Ryumin2023} %27
Ryumin, D.; Ivanko, D.; Ryumina, E. Audio-Visual Speech and Gesture Recognition by Sensors of Mobile Devices {\em Sensors} {\bf 2023}, {23(4)}

\bibitem[Sincan(2020)]{Sincan2020} %28
Sincan, O.M.; Keles, H.Y. AUTSL: A Large Scale Multi-modal Turkish Sign Language Dataset and Baseline Methods {\em CoRR} {\bf 2020}, {abs/2008.00932}

\bibitem[Jiang(2021)]{Jiang2021} %29
Jiang, S.; Sun, B.; Wang, L.; Bai, Y.; Li, K.; Fu, Y. Skeleton Aware Multi-modal Sign Language Recognition {\em CoRR} {\bf 2021}, {abs/2103.08833}

\bibitem[Peral(2022)]{Peral2022} %30
Peral,M.;  Sanfeliu,A.;  Garrell,A. Efficient Hand Gesture Recognition for Human-Robot Interactions. {\em IEEE Robotics and Automation Letters} {\bf 2022}, {\em 7}, 10272--10279.

\bibitem[Lugaresi(2019)]{Lugaresi2019} %31
Lugaresi,C.;  Tang,J.;  Nash,H.;  McClanahan,C.;  Uboweja,E.;  Hays,M.;  Zhang,F.;  Chang,C.;  Yong,M.G.;  Lee,J.;  Chang,W.;  Hua,W.;  Georg,M.;  Grundmann,M. MediaPipe: A Framework for Building Perception Pipelines. {\em CoRR} {\bf 2019}, {abs/1906.08172}

\bibitem[Dang(2022)]{Dang2022} %32
Dang,T.L.; Tran,S.D.; Nguyen,T.H.; Kim,S.; Monet,N. An improved hand gesture recognition system using keypoints and hand bounding. {\em Array} {\bf 2022}, {16}

\bibitem[Verma(2021)]{Verma2021} %33
Verma,M.; Gupta,A.; Vipparthi,S.K. One for All: An End-to-End Compact Solution for Hand Gesture Recognition. {\em CoRR} {\bf 2021}, {\\emabs/2105.07143}

\bibitem[Huang(2021)]{Huang2021} %34
Huang,Y.; Yang,J. A multi-scale descriptor for real time RGB-D hand gesture. {\em Pattern Recognition Letters} {\bf 2021}, {23}, 97--144

\bibitem[Sahoo(2022)]{Sahoo2022} %35
Sahoo,J.P.; Prakash,A.J.; Pławiak,P.; Samantray,S. Real-Time Hand Gesture Recognition Using Fine-Tuned Convolutional Neural Network. {\em Sensors} {\bf 2022}, {22}

\bibitem[Patil(2019)]{Patil2019} %36
Patil,A.R.; Subbaraman,S. Pose invariant hand gesture recognition using two stream transfer learning architecture. {\em IJEAT} {\bf 2019}, {9}, 1771--1777

\bibitem[Pinto(2019)]{Pinto2019} %37
Pinto,R.F.; Borges,C.D.B.; Almeida,A.M.A.; Paula,I.C. Static Hand Gesture Recognition Based on Convolutional Neural Networks. {\em J. Electr. Comput. Eng.} {\bf 2019}, {2019}, 1--12

\bibitem[Khosla(2020)]{Khosla2020} %38
Khosla,P.; Teterwak,P.; Wang,C.; Sarna,A.; Tian,Y.; Isola,P.; Maschinot,A.; Liu,C.; Krishnan,D. Supervised Contrastive Learning. {\em CoRR} {\bf 2020}, {abs/2004.11362}

\bibitem[Gabdrakhmanov(2019)]{Gabdrakhmanov2019} %39
Gabdrakhmanov, L.; Garaev, R.; Razinkov, E. RUSLAN: Russian Spoken Language Corpus for Speech Synthesis {\em arXiv} {\bf 2019}

\bibitem[Ronchetti(2016)]{Ronchetti2016} %40
Ronchetti, F.; Quiroga, F.; Estrebou, C.; Lanzarini, L.; Rosete, A. LSA64: A Dataset of Argentinian Sign Language {\em CACIC} {\bf 2016}

\bibitem[Joze(2018)]{Joze2018} %41
Joze, H.R.V. ; Koller, O. MS-ASL: A Large-Scale Data Set and Benchmark for Understanding American Sign Language {\em CoRR} {\bf 2018}, {1812.01053}

\bibitem[Rato(2022)]{Rato2022} %42
Rato,D.; Oliveira,M.; Santos,V.; Gomes,M.; Sappa,A. A sensor-to-pattern calibration framework for multi-modal industrial collaborative cells. {\em J. Manuf. Syst.} {\bf 2022}, {64}, 497--507

\bibitem[Quigley(2009)]{Quigley2009} %43
Quigley,M.; Conley,K.; Gerkey,B.; Faust,J.; Foote,T.; Leibs,J.; Wheeler,R.; Ng, A. ROS: an open-source Robot Operating System. {\em ICRA Workshop on Open Source Software} {\bf 2009}, {3}

\bibitem[Cubuk(2019)]{Cubuk2019} %44
Cubuk,E.D.;Zoph,B.;Shlens,J.;Le,Q.V. RandAugment: Practical data augmentation with no separate search. {\em CoRR} {\bf 2019}, {abs/1909.13719}

\bibitem[Szegedy(2015)]{Szegedy2015} %45
Szegedy,C.;Vanhoucke,V.;Ioffe,S.;Shlens,J.;Wojna,Z. Rethinking the Inception Architecture for Computer Vision. {\em CoRR} {\bf 2015}, {abs/1512.00567}

\bibitem[He(2015)]{He2015} %46
He, K.;Zhang, X.;Ren, S.;Sun, J. Deep Residual Learning for Image Recognition. {\em CoRR} {\bf CoRR},{\em abs/1512.03385}

\bibitem[Robinson(2020)]{Robinson2020} %47
Robinson, J.;Chuang, C.; Sra, S., Jegelka, S. Contrastive Learning with Hard Negative Samples. {\em CoRR} {\bf 2020}, {abs/2010.04592}

\bibitem[Scalbert(2021)]{Scalbert2021} %47
Scalbert, M.;Vakalopoulou, M.; Couzinié-Devy, Multi-Source domain adaptation via supervised contrastive learning
and confident consistency regularization. {\em CoRR} {\bf 2021}, {abs/2106.16093}

\bibitem[Kingma(2014)]{Kingma2014} %47
Kingma, D.P. ;Ba, J. Adam: A Method for Stochastic Optimization. {\em arXiv} {\bf 2014}



% @article{Du2017,
%    author = {Yu Du and Wenguang Jin and Wentao Wei and Yu Hu and Weidong Geng},
%    doi = {10.3390/s17030458},
%    issn = {14248220},
%    issue = {3},
%    journal = {Sensors (Switzerland)},
%    title = {Surface EMG-based inter-session gesture recognition enhanced by deep domain adaptation},
%    volume = {17},
%    year = {2017},
% }


% @article{Wang2018,
%    author = {Mei Wang and Weihong Deng},
%    doi = {10.1016/j.neucom.2018.05.083},
%    issn = {18728286},
%    journal = {Neurocomputing},
%    title = {Deep visual domain adaptation: A survey},
%    volume = {312},
%    year = {2018},
% }

% @article{Yang2020,
%    author = {Qiang Yang and Yu Zhang and Wenyuan Dai and Sinno Jialin Pan},
%    doi = {10.1017/9781139061773.009},
%    journal = {Transfer Learning},
%    title = {Adversarial Transfer Learning},
%    year = {2020},
% }

% @article{Rautaray2015,
%    author = {Siddharth S. Rautaray and Anupam Agrawal},
%    doi = {10.1007/s10462-012-9356-9},
%    issn = {15737462},
%    issue = {1},
%    journal = {Artificial Intelligence Review},
%    title = {Vision based hand gesture recognition for human computer interaction: a survey},
%    volume = {43},
%    year = {2015},
% }

% @article{Liu2018,
%    author = {Hongyi Liu and Lihui Wang},
%    doi = {10.1016/j.ergon.2017.02.004},
%    issn = {18728219},
%    journal = {International Journal of Industrial Ergonomics},
%    title = {Gesture recognition for human-robot collaboration: A review},
%    volume = {68},
%    year = {2018},
% }

% @article{Du2017,
%    author = {Yu Du and Wenguang Jin and Wentao Wei and Yu Hu and Weidong Geng},
%    doi = {10.3390/s17030458},
%    issn = {14248220},
%    issue = {3},
%    journal = {Sensors (Switzerland)},
%    title = {Surface EMG-based inter-session gesture recognition enhanced by deep domain adaptation},
%    volume = {17},
%    year = {2017},
% }

% @article{Zou2021,
%    author = {Yongxiang Zou and Long Cheng},
%    doi = {10.1109/TAI.2021.3098253},
%    issn = {26914581},
%    issue = {5},
%    journal = {IEEE Transactions on Artificial Intelligence},
%    title = {A Transfer Learning Model for Gesture Recognition Based on the Deep Features Extracted by CNN},
%    volume = {2},
%    year = {2021},
% }

% @article{Wu2021,
%    author = {Bi Xiao Wu and Chen Guang Yang and Jun Pei Zhong},
%    doi = {10.1007/s11633-020-1273-9},
%    issn = {17518520},
%    issue = {3},
%    journal = {International Journal of Automation and Computing},
%    title = {Research on Transfer Learning of Vision-based Gesture Recognition},
%    volume = {18},
%    year = {2021},
% }

% @article{Zhang2022,
%    author = {Yuhan Zhang and Lindong Wu and Weihua He and Ziyang Zhang and Chen Yang and Yaoyuan Wang and Ying Wang and Kun Tian and Jianxing Liao and Ying Yang},
%    doi = {10.1109/TCSII.2021.3108798},
%    issn = {15583791},
%    issue = {3},
%    journal = {IEEE Transactions on Circuits and Systems II: Express Briefs},
%    title = {An Event-Driven Spatiotemporal Domain Adaptation Method for DVS Gesture Recognition},
%    volume = {69},
%    year = {2022},
% }



% % Reference 1
% \bibitem[Author1(year)]{ref-journal}
% Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% % Reference 2
% \bibitem[Author2(year)]{ref-book1}
% Author~2, L. The title of the cited contribution. In {\em The Book Title};  Editor 1, F., Editor 2, A., Eds.;  Publishing House: City, Country, 2007;  pp. 32--58.
% % Reference 3
% \bibitem[Author3(year)]{ref-book2}
% Author 1, A.;  Author 2, B. \textit{Book Title}, 3rd ed.;  Publisher: Publisher Location, Country, 2008;  pp. 154--196.
% % Reference 4
% \bibitem[Author4(year)]{ref-unpublish}
% Author 1, A.B.;  Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted;  accepted;  in press)}.
% % Reference 5
% \bibitem[Author5(year)]{ref-communication}
% Author 1, A.B. (University, City, State, Country);  Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
% % Reference 6
% \bibitem[Author6(year)]{ref-proceeding}
% Author 1, A.B.;  Author 2, C.D.;  Author 3, E.F. Title of presentation. In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year);  Abstract Number (optional), Pagination (optional).
% % Reference 7
% \bibitem[Author7(year)]{ref-thesis}
% Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
% % Reference 8
% \bibitem[Author8(year)]{ref-url}
% Title of Site. Available online: URL (accessed on Day Month Year).
\end{thebibliography}
